Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-09 paper.tex
Add heating description to eta=10e-3 energy caption

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased.}
\label{fig:kink_str8_ke-3}%
\end{figure*}

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
\rev{Theoretical average resistive linear growth rate of flute $\gamma_r$}
& 0.35 
& 0.33
& 1.26 
& 1.25 \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\rev{Theoretical radius $\tilde{r}_s$ of peak resistive flute growth rate}
& 0.125 
& 0.125 
& 0.148 
& 0.140\\
Observed radius $r_s$ of peak flute growth rate
& 0.125 
& \rev{--} 
& 0.163 
& \rev{??}\\
\midrule
Observed axial wave number $k_{\text{flute}}$
& 23.61 
& \rev{--} 
& 16.05 
& \rev{??} \\
Observed axial wave number $k_{\text{kink}}$
& \rev{??} 
& 4.57 
& \rev{??} 
& 4.53\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$. All values
are calculated from simulations using the anisotropic model with the exception
of $k_{\text{kink}}$ which is measured from isotropic results due to noise in
the anisotropic case (the value of $k_{\text{kink}}$ appears similar, however).
The results of the isotropic cases are qualitatively similar. The radius of
peak \rev{linear flute growth rate $r_s$} is calculated at time $t=20$. The fluting wavenumber $k$ and
observed $r_s$ are measured at times just prior to the nonlinear development of
the flute instability, that is at $t=22$ when $\eta=10^{-3}$ and $t=26$ when
$\eta = 10^{-4}$. The kink wavenumber is measured at $t=26$ in both cases.
These times allow fair comparison between measurements.

>>>>

\begin{figure*}
  \centering
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy-3.pdf}
      \caption{Kinetic Energy}
      \label{fig:kink_ke-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{kinetic_energy_log-3.pdf}
      \caption{Growth rate estimation}
      \label{fig:kink_ke_log-3}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.32\textwidth}
      \includegraphics[width=\linewidth]{heating_r-3.pdf}
      \caption{Cumulative heat}
      \label{fig:heating_r-3}
    \end{subfigure}
\mycaption{Kinetic energy \rev{and heating} as a function of time in the cases where
$\eta=10^{-3}$.}{The results from both viscosity models are shown. The flute
instability appears earlier than where $\eta=10^{-4}$ and the growth rate of
the kink instability is decreased. \rev{While the heat generated via viscous heating is orders of magnitude lower when using anisotropic viscosity, Ohmic heating is enhanced by the use of the anisotropic model.}}
\label{fig:kink_str8_ke-3}%
\end{figure*}

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& 23.74
& 23.52
& 17.15
& 17.60\\
Observed axial wave number $k_{\text{flute}}$
& \rev{22.67 \pm 1}
& \rev{22.71 \pm 1}
& \rev{16.12 \pm 0.4}
& \rev{16.25 \pm 0.4}\\
Observed axial wave number $k_{\text{kink}}$
& \rev{4.57}
& \rev{4.41}
& \rev{3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

Table~\ref{tab:kink_fluting_params} summarises the quantitative differences
between the results for the two values of the resistivity $\eta$. \rev{The mean
across the radius of the ideal estimate of the growth
rate~\eqref{eq:fluting_growth_rate2} provides the theoretical average growth
rate, while the location of the peak growth rate provides a prediction of where
the instability will initially grow. This peak is used in conjunction with the
resonance equation~\eqref{eq:resonant_surface} (with $m=4$) to predict the most
unstable axial wavenumber.} The observed fluting wavenumbers are measured at
times just prior to the nonlinear development of the flute instability, that is
at $t=22$ when $\eta=10^{-3}$ and $t=26$ when $\eta = 10^{-4}$. The kink
wavenumber is measured at $t=26$ in both cases. These times allow fair
comparison between measurements. Also listed are estimates for the cumulative
heat generated via viscous and Ohmic heating during the simulation time. As is
also found in previous studies of viscous heating in kink
instabilities~\citep{quinnEffectAnisotropicViscosity2020}, anisotropic viscous
heating is approximately two orders of magnitude lower than isotropic and the
use of anisotropic viscosity enhances Ohmic heating.
